Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2019-11-21 theory.tex
Changing Model Comparison description and adding caption to plot.

>>>>

The speed at which each models reach a threshold of $90\%$ enrichment is
illustrated in Figure \ref{fig:model_comparison}. The production curve of
enrichment for each model is shown. The step functions for each model represent
the cascade configuration. Each step is one cascade in a chain of cascades and
the shape of the curve for each model gives an indication of how quickly the model
can reach the enrichment threshold. The main difference is that Model B reaches
the threshold faster, whereas Models A and C reach a higher enrichment value.
This highlights some of the immediate differences that would influence the choice
of using each model in a breakout scenario.

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.4]{ModelComparison}
    \caption{The curve of resulting product assays for each model is plotted.
    Since the feed assay of each cascade is fed into the next cascade in the
    chain, a linear relationship between the product and feed assays is plotted
    in black. The step function for each model represents the output of the
    cascade chain (each step is a cascade). While there are four steps for each
    model, Model B (green) reached the $90\%$ enrichment threshold before
    Model A (red) or Model C (blue). However, in the same amount of steps, Models
    A and C are able to achieve a higher enrichment percent than Model B.}
    \label{fig:model_comparison}
\end{figure}
